Estimating Predictive Rate-Distortion via Neural Variational Inference

### 2019-03-05 paper.tex
paper

\newcounter{theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{question}[theorem]{Question}
\newtheorem{example}[theorem]{Example}
\newtheorem{defin}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

@@

>>>>

\newcounter{theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{question}[theorem]{Question}
\newtheorem{example}[theorem]{Example}
\newtheorem{defin}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{lemma}[theorem]{Lemma}

@@

\begin{figure*}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-surp-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-16-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/LDC95T8-words-ee-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-beta-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/LDC95T8-words-logbeta-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/LDC95T8-words-logbeta-ee.pdf}
	\caption{Word-level modeling of Japanese.}\label{fig:jap-logbeta}
\end{figure*}

\begin{figure*}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-surp-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-16-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/LDC2012T05-words-ee-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-beta-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/LDC2012T05-words-logbeta-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/LDC2012T05-words-logbeta-ee.pdf}
	\caption{Word-level modeling of Chinese.}\label{fig:jap-logbeta}
\end{figure*}

\begin{figure*}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-surp-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-16-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/ar-words-ee-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-beta-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/ar-words-logbeta-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/ar-words-logbeta-ee.pdf}
	\caption{Word-level modeling of Arabic.}\label{fig:jap-logbeta}
\end{figure*}

\begin{figure*}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-surp-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-16-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/LDC95T8-words-ee-mem.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/ru-words-beta-mem.pdf}
\includegraphics[width=0.3\textwidth]{code/figures/LDC95T8-words-nlogbeta-mem-fitted.pdf}
%\includegraphics[width=0.3\textwidth]{code/figures/LDC95T8-words-logbeta-ee.pdf}
	\caption{Word-level modeling of Japanese.}\label{fig:jap-logbeta-fit}
\end{figure*}
